Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-05-11 paper.tex
Formatting fixes
More about acceptance criterion

\begin{figure*}
  \centering
  \subfigure[Surface-surface function calculated for a ball with radius
    $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
    \label{fig:fss-ball}}
  \hfill
  \subfigure[Surface-void function calculated for a disk with radius
    $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
    \label{fig:fsv-disk}}
  \hfill
  \subfigure[Surface-void function calculated for a ball with radius
    $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
    \label{fig:fsv-ball}}
  \caption[]{Comparison of filters $H$ and $H'$ for cases in which newly
    developed algorithms \cref{sec:fss-2d}, \cref{sec:fsss-3d} are not
    applicable. Theoretical curves are provided for each case.}
  \label{fig:not-covered}
\end{figure*}
With the new filter calculation of $F_{ss}$ becomes more precise also for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve. It can be verified that filter $H'$ is better indeed by
calculating
\begin{equation*}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
\end{equation*}
where $x_i$ belong to a set
$(\epsilon, 2R - \epsilon) \cup (2R + \epsilon, 1)$. Taking $\epsilon = 0.01$ we
get $error = 0.006$ for filter $H$ and $error = 0.00017$ for filter
$H'$. Calculation of surface-void function also benefits from the new filter
(\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).

Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
$H$ has faster convergence with increase of image resolution. Our
acceptance criterion developed in \textcolor{red}{cite our paper again} works
also for $H'$, but sometimes it's possible to calculate a poor estimate of
$F_{ss}$ using $H$ but not $H'$. Secondly, $H'$ behaves worse that $H$ in points
of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.

>>>>

\begin{figure*}
  \centering
  \subfigure[Surface-surface function calculated for a ball with radius
    $R = 0.24$. Image dimensions are  $450 \times 450 \times 450$.]{
    \includegraphics[width=0.3\linewidth]{images/ball-3d-ss.png}
    \label{fig:fss-ball}}
  \hfill
  \subfigure[Surface-void function calculated for a disk with radius
    $R = 0.2$. Image dimensions are $2000 \times 2000$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-disk.png}
    \label{fig:fsv-disk}}
  \hfill
  \subfigure[Surface-void function calculated for a ball with radius
    $R = 0.2$. Image dimensions are $300 \times 300 \times 300$.]{
    \includegraphics[width=0.3\linewidth]{images/fsv-ball.png}
    \label{fig:fsv-ball}}
  \caption[]{Comparison of filters $H$ and $H'$ for cases in which newly
    developed algorithms \cref{sec:fss-2d}, \cref{sec:fsss-3d} are not
    applicable. Theoretical curves are provided for each case.}
  \label{fig:not-covered}
\end{figure*}
With the new filter calculation of $F_{ss}$ becomes more precise also for
three-dimensional images. This can be seen in comparison with theoretical values
for known cases like the one of a ball. On \cref{fig:fss-ball} there are plots
of $F_{ss}$ function calculated with filters $H$ and $H'$ along with a
theoretical curve. It can be verified that filter $H'$ is better indeed by
calculating
\begin{equation}
  error = \sqrt{\frac{\sum_i (F_{ss}^{calc}(x_i) -
      F_{ss}^{theory}(x_i))^2}{\sum_i F_{ss}^{theory}(x_i)^2}}
  \label{eq:error}
\end{equation}
where $x_i$ belong to a set $(\epsilon, 2R - \epsilon)$. Taking
$\epsilon = 0.01$ we get $error = 0.05$ for filter $H$ and $error = 0.03$ for
filter $H'$. Calculation of surface-void function also benefits from the new
filter (\cref{fig:fsv-disk}, \cref{fig:fsv-ball}).

Unfortunately the filter $H'$ has some drawbacks in comparison with $H$. Firstly
$H$ has faster convergence with increase of image resolution. Our
acceptance criterion $C_{0.5} > 0.97$ developed in \textcolor{red}{cite our
  paper again} works also for $H'$, but sometimes when the criterion is not
satisfied, it's possible to calculate a poor estimate of $F_{ss}$ using $H$ but
not $H'$. For example, consider images of a disk used for calculation of
$F_{ss}$ on \cref{fig:fss-disk}. In \cref{table:crit} we provide values of
$C_{0.5}$ criterion and errors \cref{eq:error} for filters $H$ and $H'$.

Secondly, $H'$ behaves worse that $H$ in points
of discontinuity of $F_{ss}$ as can be seen on \cref{fig:fss-disk}.

\begin{table}[h!]
  \centering
  \begin{tabular}{|c | c | c | c|}
    \hline
    Dimensions & $C_{0.5}$ & Error ($H$) & Error ($H'$) \\
    \hline
    $100 \times 100$ & 0.822 & 0.178 & 0.408 \\
    \hline
    $400 \times 400$ & 0.921 & 0.072 & 0.098 \\
    \hline
    $3100 \times 3100$ & 0.972 & 0.049 & 0.009 \\
    \hline
  \end{tabular}
  \caption{$C_{0.5}$ criterion and relative errors in computation of $F_{ss}$
    for filters $H$ and $H'$. The case with a disk. Plots of $F_{ss}$ functions
    can be seen on \cref{fig:fss-disk}.}
  \label{table:crit}
\end{table}
